---
title: "Insitu_MassivePorites"
author: "Colin Anthony"
date: '2022-08-09'
output: pdf_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE) 

library(pacman)
pacman::p_load(lattice, rcompanion, FSA, plyr, dplyr, readxl, vegan, factoextra,
               FD, tidyverse, sem, ggplot2, ggpubr, ggExtra, ggtext, patchwork,
               paletteer, scales, nptest, rstatix, RColorBrewer, gridExtra)

PoritesSurveyData <- read_excel("C:/Users/colin/Downloads/PoritesSurveyData.xlsx", 
                                sheet = "DATA (2)", col_types = c("text", 
                                                              "text", "text", 
                                                              "numeric", "text", 
                                                              "text", "numeric",
                                                              "numeric","numeric", 
                                                              "numeric","numeric", 
                                                              "numeric","numeric",
                                                              "numeric","numeric", 
                                                              "numeric", "text"))

PoritesSurveyData <- subset(PoritesSurveyData, Species == "Mass")
PoritesSurveyData <- subset(PoritesSurveyData, SizeClass != "0")
PoritesSurveyData <- subset(PoritesSurveyData, Color != "bb")
PoritesSurveyData <- subset(PoritesSurveyData, Color != "g")
PoritesSurveyData$Color <- recode(PoritesSurveyData$Color, y = "brown", 
                                  b = "brown", bp = "brown/purple", p = "purple")

PoritesSurveyData$DepthFactor <- recode(PoritesSurveyData$Depth, "1" = "1-2 m", 
                                        "2" = "1-2 m", "3" = "3-5 m", "4" = "3-5 m", 
                                        "5" = "3-5 m", "6" = "3-5 m","8" = "8-10 m", 
                                        "9" = "8-10 m", "10" = "8-10 m", 
                                        "15" = "15-18 m", "18" = "15-18 m")
PoritesSurveyData$Depth <- recode(PoritesSurveyData$Depth, "1" = "1", "2" = "1",
                                  "3" = "3", "4" = "3", "5" = "3", "6" = "3",
                                  "8" = "10", "9" = "10", "10" = "10", "15" = "15", 
                                  "18" = "15")

PoritesSurveyData$ReefType <- recode(PoritesSurveyData$Site, 
                                     "Babi Island" = "Fore reef", "Haputo" = "Fore reef", 
                                     "Ypao" = "Fore reef", "Luminao" = "Reef flat", 
                                     "Piti West" = "Reef flat", "Tumon" = "Reef flat")

CleanMassives <- PoritesSurveyData

CleanMassives$Depth <- as.numeric(CleanMassives$Depth)
CleanMassives$Depth <- factor(CleanMassives$Depth, levels=c('1','3','10','15'))

Size_Class <- ggplot(CleanMassives, aes(SizeClass))+
  geom_bar(aes(fill = Color), position = "stack")+
  theme_classic()+
  theme(legend.position = "bottom")+
  facet_grid(cols = vars(Depth), rows = vars(Site))+
  ggtitle("Size")
Size_Class
```

```{r}
## Non-parametric Correlation Test to separate reef types as a compounding factor
Matrix <- CleanMassives
#Produce a numeric matrix
Matrix <- select(Matrix, Recorder, Site, ReefType, Depth, Color, SizeClass, 
                 PartMort, TotalDisease)

Matrix$Recorder <- recode(Matrix$Recorder, "BB" = "1", "CA" = "2", "CL" = "3", 
                          "CT" = "4", "GM" = "5", "LJR" = "6", "MA" = "7", "TM" = "8")
Matrix$Site <- recode(Matrix$Site, "Babi Island" = "1", "Haputo" = "2", "Luminao" = "3", 
                      "Piti West" = "4", "Tumon" = "5", "Ypao" = "6")
Matrix$ReefType <- recode(Matrix$ReefType, "Reef flat" = "1", "Fore reef" = "2")
Matrix$Color <- recode(Matrix$Color, "brown" = "1", "brown-purple" = "2", "purple" = "3")
Matrix$TotalDisease <- recode(Matrix$TotalDisease, "0" = "0", "1" ="1", "2" = "1", 
                              "3" = "1", "4" = "1", "5" = "1", "6" = "1", "7" = "1")

#View(Matrix)
Matrix$Recorder <- as.numeric(Matrix$Recorder)
Matrix$Site <- as.numeric(Matrix$Site)
Matrix$ReefType <- as.numeric(Matrix$ReefType)
Matrix$Color <- as.numeric(Matrix$Color)
Matrix$TotalDisease <- as.numeric(Matrix$TotalDisease)
Matrix$Depth <- as.numeric(Matrix$Depth)

```

```{r}

matrixfore <- subset(Matrix, ReefType != 1)
matrixflat <- subset(Matrix, ReefType != 2)
matrixfore <- select(matrixfore, Recorder, Site, Depth, Color, SizeClass, 
                     PartMort, TotalDisease)
matrixflat <- select(matrixflat, Recorder, Site, Color, SizeClass, PartMort, 
                     TotalDisease)

par(mfrow=c(1,2))
#Reef Flat exclusive correlations
cor.matflat <- cor_mat(matrixflat, method = "spearman",  
                       alternative = "two.sided", conf.level = 0.99)
cor.matflat %>%
  cor_reorder() %>%
  pull_lower_triangle() %>%
  cor_plot(label = TRUE)

statisticaloutputflat <- cor_gather(cor.matflat)
statisticaloutputflat %>% as_tibble %>% print(n = nrow(.))

#Forereef exclusive correlations
cor.matfore <- cor_mat(matrixfore, method = "spearman",  
                       alternative = "two.sided", conf.level = 0.99)
cor.matfore %>%
  cor_reorder() %>%
  pull_lower_triangle() %>%
  cor_plot(label = TRUE)

statisticaloutputfore <- cor_gather(cor.matfore)
statisticaloutputfore %>% as_tibble %>% print(n = nrow(.))
```

First plot is for reef flats; Second plot is for forereefs

```{r}

## Compare CA and CL directly for the most consistent biological correlations

#CA
O2<- subset(Matrix, Recorder == "2")
O2 <- O2[complete.cases(O2), ]
O2$Recorder <- NULL
O2$ReefType <- NULL

#CL
O3<- subset(Matrix, Recorder == "3")
O3 <- O3[complete.cases(O3), ]
O3$Recorder <- NULL
O3$ReefType <- NULL

par(mfrow=c(1,2))
cor.O2 <- cor_mat(O2, method = "spearman",  
                  alternative = "two.sided", conf.level = 0.99)
cor.O2 %>%
  cor_reorder() %>%
  pull_lower_triangle() %>%
  cor_plot(label = TRUE)

statisticaloutputfore <- cor_gather(cor.matfore)
statisticaloutputfore %>% as_tibble %>% print(n = nrow(.))

cor.O3 <- cor_mat(O3, method = "spearman",  
                  alternative = "two.sided", conf.level = 0.99)
cor.O3 %>%
  cor_reorder() %>%
  pull_lower_triangle() %>%
  cor_plot(label = TRUE)

statisticaloutputfore <- cor_gather(cor.matfore)
statisticaloutputfore %>% as_tibble %>% print(n = nrow(.))

```

```{r}
#Recorder removed
MatrixNoRecorder = subset(Matrix, select = -c(Recorder, Site, ReefType) )

par(mfrow=c(1,2))
cor.matfinal <- cor_mat(MatrixNoRecorder, method = "spearman",  
                        alternative = "two.sided", conf.level = 0.999)
cor.matfinal %>%
  pull_lower_triangle() %>%
  cor_plot(label = TRUE)
statisticaloutput <- cor_gather(cor.matfinal)
statisticaloutput %>% as_tibble %>% print(n = nrow(.))
```
The total Spearman's rho analysis has confirmed a real correlation between size class, mortality, and disease
This was used to inform tests of differences across depth and color.

```{r, results='hide', fig.keep='all'}

#Plot the strongest and most consistent correlations (Figure 2)

CleanMassives$SizeClass <- as.numeric(CleanMassives$SizeClass)
CleanMassives$PartMort <- as.numeric(CleanMassives$PartMort)
red_beard<- ggplot(CleanMassives, aes(x = SizeClass, y = PartMort)) +
  geom_boxplot(aes(group = SizeClass), outlier.shape = NA)+
  geom_point(alpha = 0.0) +
  geom_jitter(alpha = 0.05)+
  xlab(label = "Size class")+
  ylab(label = "Partial mortality")+
  ggtitle("A")+
  annotate('text', x = 5.5, y = 5.5, label = "~rho~{}==0.48 ",
           parse = TRUE, size=5)+
  scale_x_continuous(breaks = c(1,2,3,4,5,6))+
  scale_y_continuous(breaks = c(0,1,2,3,4,5,6))+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 12), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold", vjust = -1), 
        panel.grid.minor = element_blank())

SizeMort <- ggMarginal(red_beard, type = "histogram")

CleanMassives$TotalDisease[CleanMassives$TotalDisease > 0] <- 1

SizeDis <- ggplot(CleanMassives, aes(x = SizeClass, y = TotalDisease)) +
  geom_boxplot(aes(group = TotalDisease, horizontal = TRUE), outlier.shape = NA)+
  #geom_point(alpha = 1) +
  geom_jitter(alpha = 0.04)+
  xlab(label = "Size class")+
  ylab(label = "Active disease")+
  ggtitle("C")+
  annotate('text', x = 5.2, y = 1.2, label = "~rho~{}==0.2 ",parse = TRUE, size=5)+
  scale_x_continuous(breaks = c(1,2,3,4,5,6))+
  scale_y_continuous(breaks = c(0,1))+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 12), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), 
        panel.grid.minor = element_blank())

MortDis <- ggplot(CleanMassives, aes(x = PartMort, y = TotalDisease)) +
  geom_boxplot(aes(group = TotalDisease), outlier.shape = NA)+
  #geom_point(alpha = 1) +
  geom_jitter(alpha = 0.04)+
  xlab(label = "Partial mortality")+
  ylab(label = "Active disease")+
  ggtitle("B")+
  annotate('text', x = 5, y = 1.2, label = "~rho~{}==0.18 ",parse = TRUE, size=5)+
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6))+
  scale_y_continuous(breaks = c(0,1))+
  theme_minimal()+
  theme(axis.text.x = element_text(size = 12), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), 
        panel.grid.minor = element_blank())
  
Disease <- gridExtra::grid.arrange(MortDis, SizeDis, nrow = 2)
gridExtra::grid.arrange(SizeMort, Disease, nrow = 1)
```

```{r}
#Test for population level differences across depth
CleanMassives$SizeClass <- as.numeric(CleanMassives$SizeClass)
CleanMassives$Depth <- factor(CleanMassives$Depth, levels=c('1','3','10','15'))
CleanMassives$Depth <- as.numeric(CleanMassives$Depth)
CleanMassives$Depth <- as.character(CleanMassives$Depth)
head(CleanMassives)
kruskal.test(SizeClass ~ Depth, data = CleanMassives)

histogram(~ SizeClass | Depth,
          data=CleanMassives,
          layout=c(1,4)) 
boxplot(SizeClass ~ Depth, data = CleanMassives)

DistStats = dunnTest(SizeClass ~ Depth, data = CleanMassives, method = "bh")
DistStats
DistStats = DistStats$res
DistStats
cldList(comparison = DistStats$Comparison,
        p.value    = DistStats$P.adj,
        threshold  = 0.001)
```

```{r}
#Plot distributions, get colony counts, and color ratios...
#now that we've identified it as a statistically supported pattern

CleanMassives$Depth <- as.numeric(CleanMassives$Depth)
CleanMassives$DepthFactor = factor(CleanMassives$DepthFactor, 
                                   levels=c('1-2 m','3-5 m','8-10 m','15-18 m'))

Counts <- ggplot(CleanMassives, aes(SizeClass, fill = Color))+
  geom_bar(position = position_stack(reverse = TRUE))+
  theme_classic()+
  ylab('Counts')+
  xlab('Size-class')+
  theme(legend.position = "none")+
  scale_fill_manual(values = c("#d1bb3d","#45384a", "#af7bc7"), 
                    name = "Color morph", labels = c("brown", "hybrid", "purple")) +
  theme(axis.text.x = element_text(size = 12), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), 
        legend.title = element_text(size = 14), 
        legend.text = element_text(size = 12), strip.text.x = element_text(size = 14))+
  facet_grid(cols = vars(DepthFactor))
Counts

#Colony counts for each size class across the shallowest and deepest transects
sum(with(CleanMassives, Depth == "1"))
sum(with(CleanMassives, Depth == "4"))

sum(with(CleanMassives, Depth == "1" & SizeClass == "6"))
sum(with(CleanMassives, Depth == "4" & SizeClass == "6"))
sum(with(CleanMassives, Depth == "1" & SizeClass == "5"))
sum(with(CleanMassives, Depth == "4" & SizeClass == "5"))
sum(with(CleanMassives, Depth == "1" & SizeClass == "4"))
sum(with(CleanMassives, Depth == "4" & SizeClass == "4"))
sum(with(CleanMassives, Depth == "1" & SizeClass == "3"))
sum(with(CleanMassives, Depth == "4" & SizeClass == "3"))
sum(with(CleanMassives, Depth == "1" & SizeClass == "2"))
sum(with(CleanMassives, Depth == "4" & SizeClass == "2"))
sum(with(CleanMassives, Depth == "1" & SizeClass == "1"))
sum(with(CleanMassives, Depth == "4" & SizeClass == "1"))
head(CleanMassives)
RatioFacet <- ggplot(CleanMassives, aes(SizeClass, fill = Color))+
  geom_bar(position = position_fill(reverse = TRUE), stat = "count")+
  geom_text(aes(label = paste0(..count..)), stat = 'count', 
            position = position_fill(reverse = TRUE, vjust = 0.5), 
            size = 3, color = "white", face = "bold")+
  theme_classic()+
  ylab('Rel Abun')+
  xlab('Depth')+
  theme(legend.position = "bottom")+
  scale_fill_manual(values = c("#d1bb3d","#45384a", "#af7bc7"), 
                    name = "Color morph", labels = c("brown", "hybrid", "purple")) +
  theme(axis.text.x = element_text(size = 12), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), 
        legend.title = element_text(size = 14), 
        legend.text = element_text(size = 12), 
        strip.text.x = element_text(size = 14))+
  facet_grid(cols = vars(DepthFactor))
RatioFacet

Ratio <- ggplot(CleanMassives, aes(DepthFactor, fill = Color))+
  geom_bar(position = position_fill(reverse = TRUE), stat = "count")+
  geom_text(aes(label = paste0(..count..)), stat = 'count', 
            position = position_fill(reverse = TRUE, vjust = 0.5), size = 3, 
            color = "white", face = "bold")+
  theme_classic()+
  ylab('Rel Abun')+
  xlab('Depth')+
  theme(legend.position = "bottom")+
  scale_fill_manual(values = c("#d1bb3d","#45384a", "#af7bc7"), 
                    name = "Color morph", labels = c("brown", "hybrid", "purple")) +
  theme(axis.text.x = element_text(size = 12), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), 
        legend.title = element_text(size = 14), 
        legend.text = element_text(size = 12), 
        strip.text.x = element_text(size = 14))
Ratio
#Color ratios at each depth

```

```{r}
##Initial comparison of means to compare mortality across depth
CleanMassives$PartMort <- as.numeric(CleanMassives$PartMort)
CleanMassives$Depth <- factor(CleanMassives$Depth)

kruskal.test(PartMort ~ Depth, data = CleanMassives)

histogram(~ PartMort | Depth,
          data=CleanMassives,
          layout=c(1,4)) 
          
boxplot(PartMort ~ Depth, data = CleanMassives)

DistStats = dunnTest(PartMort ~ Depth, data = CleanMassives, method = "bh")
DistStats
DistStats = DistStats$res
DistStats
cldList(comparison = DistStats$Comparison,
        p.value    = DistStats$P.adj,
        threshold  = 0.001)
```

This suggests an interaction, as did the Spearman correlation, but confounding factors may be biasing results.
Groupings also suggest that depth is not what causes statistical differences.
```{r}
###Subset each colony size to see if the relationship between mortality and depth is real
#or if it is simply a byproduct of the colony size class distributions
Size1 <- subset(CleanMassives, SizeClass == "1")
kruskal.test(PartMort ~ Depth, data = Size1)

DistStats = dunnTest(PartMort ~ Depth, data = Size1, method = "bh")
DistStats
DistStats = DistStats$res
DistStats
cldList(comparison = DistStats$Comparison,
        p.value    = DistStats$P.adj,
        threshold  = 0.001)

Size2 <- subset(CleanMassives, SizeClass == "2")
kruskal.test(PartMort ~ Depth, data = Size2)

Size3 <- subset(CleanMassives, SizeClass == "3")
kruskal.test(PartMort ~ Depth, data = Size3)

Size4 <- subset(CleanMassives, SizeClass == "4")
kruskal.test(PartMort ~ Depth, data = Size4)

Size5 <- subset(CleanMassives, SizeClass == "5")
kruskal.test(PartMort ~ Depth, data = Size5)

Size6 <- subset(CleanMassives, SizeClass == "6")
kruskal.test(PartMort ~ Depth, data = Size6)
```        
        
These tests confirm that size class differences across depth were confounding 
our partial mortality results.
The removal of size class as a contributing factor revealed little to no 
difference in the amount of partial mortality at each depth.

```{r}
kruskal.test(TotalDisease ~ Depth, data = Size1)

DistStats = dunnTest(TotalDisease ~ Depth, data = Size1, method = "bh")
DistStats
DistStats = DistStats$res
DistStats
cldList(comparison = DistStats$Comparison,
        p.value    = DistStats$P.adj,
        threshold  = 0.001)

kruskal.test(TotalDisease ~ Depth, data = Size2)

DistStats = dunnTest(TotalDisease ~ Depth, data = Size2, method = "bh")
DistStats
DistStats = DistStats$res
DistStats
cldList(comparison = DistStats$Comparison,
        p.value    = DistStats$P.adj,
        threshold  = 0.001)

kruskal.test(TotalDisease ~ Depth, data = Size3)

DistStats = dunnTest(TotalDisease ~ Depth, data = Size3, method = "bh")
DistStats
DistStats = DistStats$res
DistStats
cldList(comparison = DistStats$Comparison,
        p.value    = DistStats$P.adj,
        threshold  = 0.001)

kruskal.test(TotalDisease ~ Depth, data = Size4)
#Not significant
kruskal.test(TotalDisease ~ Depth, data = Size5)
#Not significant
kruskal.test(TotalDisease ~ Depth, data = Size6)
#Not significant
```

```{r}
#Color-specific comparison of functional traits
CleanMassives$Depth <- as.numeric(CleanMassives$Depth)
kruskal.test(Depth ~ Color , data = CleanMassives)

histogram(~ Depth | Color,
          data=CleanMassives,
          layout=c(1,3)) 
boxplot(Depth ~ Color, data = CleanMassives)
CleanMassives$Depth <- as.numeric(CleanMassives$Depth)
DepthStats = dunnTest(Depth ~ Color, data = CleanMassives, method = "bh")
DepthStats
DepthStats = DepthStats$res
DepthStats

cldList(comparison = DepthStats$Comparison,
        p.value    = DepthStats$P.adj,
        threshold  = 0.001)

kruskal.test(PartMort ~ Color, data = CleanMassives)

histogram(~ PartMort | Color,
          data=CleanMassives,
          layout=c(3,3)) 
boxplot(PartMort ~ Color, data = CleanMassives)

MortStats = dunnTest(PartMort ~ Color, data = CleanMassives, method = "bh")
MortStats
MortStats = MortStats$res
MortStats

cldList(comparison = MortStats$Comparison,
        p.value    = MortStats$P.adj,
        threshold  = 0.001)

kruskal.test(SizeClass ~ Color, data = CleanMassives)

histogram(~ SizeClass | Color,
          data=CleanMassives,
          layout=c(1,3)) 
boxplot(SizeClass ~ Color, data = CleanMassives)
SizeStats = dunnTest(SizeClass ~ Color, data = CleanMassives, method = "bh")
SizeStats
SizeStats = SizeStats$res
SizeStats

cldList(comparison = SizeStats$Comparison,
        p.value    = SizeStats$P.adj,
        threshold  = 0.001)

##Needs to be changed to a binary code
CleanMassives$TotalDisease[CleanMassives$TotalDisease > 0] <- 1

#View(CleanMassives)
kruskal.test(TotalDisease ~ Color, data = CleanMassives)

histogram(~ TotalDisease | Color,
          data=CleanMassives,
          layout=c(1,3)) 
boxplot(TotalDisease ~ Color, data = CleanMassives)

DisStats = dunnTest(TotalDisease ~ Color, data = CleanMassives, method = "bh")
DisStats
DisStats = DisStats$res
DisStats

cldList(comparison = DisStats$Comparison,
        p.value    = DisStats$P.adj,
        threshold  = 0.001)
```

```{r}
#Color functional difference plots
Hybrid <- c("brown", "hybrid", "purple")

CleanMassives$Depth <- as.character(CleanMassives$Depth)
Depth <- ggplot(CleanMassives, aes(Color, group = Depth, fill = Depth))+
  geom_bar(position = "fill")+
  theme_classic()+
  ylab("Relative abundance")+
  scale_x_discrete(labels= Hybrid)+
  theme(legend.position = "bottom")+
  scale_fill_grey(start = 0.7, end = 0, 
                  labels=c('1-2 m','3-5 m','8-10 m','15-18 m'), name = "Depth (m)")+
  theme(axis.text.x = element_text(size = 12, angle = -45), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), 
        legend.title = element_text(size = 12), 
        legend.text = element_text(size = 11))+
  guides(fill = guide_legend(nrow = 2, title.position="top"))+
  ggtitle("A")

CleanMassives$SizeClass <- as.character(CleanMassives$SizeClass)
Size <- ggplot(CleanMassives, aes(Color, group = SizeClass, fill = SizeClass))+
  geom_bar(position = position_fill(reverse = TRUE))+
  theme_classic()+
  ylab('')+
  theme(legend.position = "bottom")+
  scale_x_discrete(labels= Hybrid)+
  scale_fill_grey(name = "Size-class")+
  theme(axis.text.x = element_text(size = 12, angle = -45), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), legend.title = element_text(size = 12), legend.text = element_text(size = 11))+
  guides(fill = guide_legend(nrow = 2, title.position="top"))+
  ggtitle("B")

CleanMassives$PartMort <- as.character(CleanMassives$PartMort)
CleanMassives <- CleanMassives[complete.cases(CleanMassives), ]

Mortality <- ggplot(CleanMassives, aes(Color, group = PartMort, fill = PartMort))+
  geom_bar(position = position_fill(reverse = TRUE))+
  theme_classic()+
  ylab('')+
  theme(legend.position = "bottom")+
  scale_fill_grey(name = "Mortality")+
  scale_x_discrete(labels= Hybrid)+
  theme(axis.text.x = element_text(size = 12, angle = -45), axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 11))+
  guides(fill = guide_legend(nrow = 2, title.position="top"))+
  ggtitle("C")

CleanMassives$TotalDisease <- as.character(CleanMassives$TotalDisease)
Dis <- ggplot(CleanMassives, aes(Color, group = TotalDisease, fill = TotalDisease))+
  geom_bar(position = position_fill(reverse = TRUE))+
  theme_classic()+
  theme(legend.position = "bottom")+
  scale_fill_grey(name = "Disease")+
  ylab('')+
  scale_x_discrete(labels= Hybrid)+
  theme(axis.text.x = element_text(size = 12, angle = -45), 
        axis.title.x = element_text(size = 14),
        axis.text.y = element_text(size = 12), axis.title.y = element_text(size = 14),
        plot.title = element_text(size = 14, face = "bold"), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 11))+
  guides(fill = guide_legend(nrow = 2, title.position="top"))+
  ggtitle("D")
grid.arrange(Depth, Size, Mortality, Dis, nrow = 1)
```